### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
Regmachine: hopefully I got the articles right

The program order relation tracks precedence of events within a single thread. 
The reads-from relation captures the flow of values from 
write events to read events, and ensures that values 
do not appear out of thin-air~\cite{Boehm-Demsky:MSPC14, Lahav-al:PLDI17}.

@@

Finally, we need a way to reconcile the event structure
with the states of machine's threads. 
To do so we use a function ${\thrdmap : \eventSet \fun \ThrdState}$
which maps event to a thread state obtained as a result of
execution of event's side-effect.

>>>>

The program order relation tracks precedence of events within a single thread. 
The reads-from relation captures the flow of values from 
write events to read events, and ensures that values 
do not appear out of thin air~\cite{Boehm-Demsky:MSPC14, Lahav-al:PLDI17}.

@@

Finally, we need a way to reconcile the event structure
with the states of machine's threads. 
To do so we use a function ${\thrdmap : \eventSet \fun \ThrdState}$
which maps an event to a thread state obtained as the result of
the execution of the event's side-effect.
